---
title: "Nielsen Part2"
author: "Weijie Gao"
date: "31 May 2017"
output: html_document
---
```{r}
dataPath <- "C:/Users/AA/Google Drive/UChicago MscA_/Marketing Analytics/Course Project/Nielsen/2012/"
product.data <- read.delim(file=paste(dataPath,'products_extra_2012.tsv',sep='/'),header=TRUE,sep="\t")

panelists_2012 <- read.delim(file=paste(dataPath,'panelists_2012.tsv',sep='/'),header=TRUE,sep="\t")

purchases_2012 <- read.delim(file=paste(dataPath,'purchases_2012.tsv',sep='/'),header=TRUE,sep="\t")

trips_2012 <- read.delim(file=paste(dataPath,'trips_2012.tsv',sep='/'),header=TRUE,sep="\t")

household_purchase <- merge(purchases_2012, trips_2012, by = "trip_code_uc")

YOGURT_2012 <- product.data[product.data$product_descr=="YOGURT",c(1:5,15:19)]
YOGURT_purchase <- merge(household_purchase,YOGURT_2012,by="upc")

#dataPath <- "~/Documents/Marketing_project/latest"
brand.data <- read.delim(file=paste(dataPath,'brand_variations.tsv',sep='/'),header=TRUE,sep="\t")
product.data.latest <- read.delim(file=paste(dataPath,'products.tsv',sep='/'),header=FALSE,sep="\t")
retailers.data <- read.delim(file=paste(dataPath,'retailers.tsv',sep='/'),header=TRUE,sep="\t")

# delete rows where the total price paid is 0
YOGURT_purchase <- YOGURT_purchase[!(YOGURT_purchase$total_price_paid==0),]
# YOGURT_purchase <- YOGURT_purchase[!(YOGURT_purchase$total_price_paid==0&YOGURT_purchase$deal_flag_uc==0),]
write.table(YOGURT_purchase, "YOGURT_purchase.csv", sep=",", na = "", row.names = FALSE)

# Quantity and total price sold for different yogurt styles
sales_style <- aggregate(YOGURT_purchase[,c(4,5)],by=list(YOGURT_purchase$style_descr),FUN=sum)
sales_style.sorted <- sales_style[order(-sales_style$quantity),]
colnames(sales_style.sorted)[1] <- "Style"
write.table(sales_style.sorted, "sales_style.sorted.csv", sep=",", na = "", row.names = FALSE)

# Quantity and total price sold for different yogurt types
sales_type <- aggregate(YOGURT_purchase[,c(4,5)],by=list(YOGURT_purchase$type_descr),FUN=sum)
sales_type.sorted <- sales_type[order(-sales_type$quantity),]
colnames(sales_type.sorted)[1] <- "Type"
write.table(sales_type.sorted, "sales_type.sorted.csv", sep=",", na = "", row.names = FALSE)

# Quantity and total price sold for different yogurt flavor
sales_flavor <- aggregate(YOGURT_purchase[,c(4,5)],by=list(YOGURT_purchase$flavor_descr),FUN=sum)
sales_flavor.sorted <- sales_flavor[order(-sales_flavor$quantity),]
colnames(sales_flavor.sorted )[1] <- "Flavor"

# find the index for a specific column names
grep("unit_price", colnames(YOGURT_purchase))
grep("coupon_value", colnames(YOGURT_purchase))
grep("deal_flag_uc",colnames(YOGURT_purchase))
grep("retailer_code",colnames(YOGURT_purchase))
grep("flavor_code",colnames(YOGURT_purchase))
grep("type_code",colnames(YOGURT_purchase))

# choose the selected columns
yogurt_selected <- YOGURT_purchase[,c(4,5,8,9,6,7,10,17,20)]

# look at the column names and their classes
sapply(yogurt_selected,class)

# change the deal_flag_uc, flavor_code, type_code into factor
yogurt_selected$deal_flag_uc <- as.factor(yogurt_selected$deal_flag_uc)
yogurt_selected$flavor_code <- as.factor(yogurt_selected$flavor_code)
yogurt_selected$type_code <- as.factor(yogurt_selected$type_code)
yogurt_selected$retailer_code <- as.factor(yogurt_selected$retailer_code)
summary(yogurt_selected)

```
```{r}
# Analysis of Promotion Effectiveness
# divide the dataset into two sub dataset by ad_type
sales_nonpro <- subset(YOGURT_purchase,deal_flag_uc==0)
sales_pro <- subset(YOGURT_purchase,deal_flag_uc==1)

#calculate the mean of sales with different deal_flag_uc
mean(sales_nonpro$quantity)
mean(sales_pro$quantity)
```
The mean of sales without promotion is about 1.96; the mean of sales with promotion is about 2.48. It looks like that the latter one is better. To find out how likely the conclusion is correct for the whole population, it is necessary to do statistical testing – two-sample t-test.
```{r}
par(mfrow = c(1,2))
# histogram to explore the data distribution shapes
hist(sales_nonpro$quantity,main='',xlab='sales with nature production theme ad',prob=T)
hist(sales_pro$quantity,main='',xlab='sales with family health caring theme ad',prob=T)

hist(log(sales_nonpro$quantity),main='',xlab='sales with nature production theme ad',prob=T)
hist(log(sales_pro$quantity),main='',xlab='sales with family health caring theme ad',prob=T)

t.test(log(sales_nonpro$quantity),log(sales_pro$quantity))
```
```{r}
# aggregate the yogurt purchase data by different style
style_aggregated <- aggregate(YOGURT_purchase[,c(4,5,6,7)],by=list(YOGURT_purchase$style_descr),FUN=sum)
style_aggregated$unit_price <- style_aggregated$total_price_paid/style_aggregated$quantity
head(style_aggregated)
style_aggregated_sorted<- style_aggregated[order(-style_aggregated$quantity),]

hist(style_aggregated_sorted$unit_price,main="",xlab="unit price",prob=T)
hist(log(style_aggregated_sorted$unit_price),main="",xlab="unit price",prob=T,col="lightblue")

hist(log(style_aggregated_sorted$quantity),main="",xlab="quantity",prob=T,col="lightblue")

hist(log(style_aggregated_sorted$coupon_value),main="",xlab="quantity",prob=T,col="lightblue")

log_quantity <- log(style_aggregated_sorted$quantity+0.0001)
log_unit_price <- log(style_aggregated_sorted$unit_price+0.0001)
log_coupon_value <- log(style_aggregated_sorted$coupon_value+0.0001)
deal_flag_uc<- style_aggregated_sorted$deal_flag_uc

m1 <- lm(log_quantity ~ log_unit_price+log_coupon_value,data=style_aggregated_sorted)
summary(m1)
m2 <- lm(log_quantity ~ log_unit_price+log_coupon_value+deal_flag_uc,data=style_aggregated_sorted)
summary(m2)

# Check the residuals assumption
par(mfrow=c(2,2))
plot(m2)

# check the multicollinearity among the variables 
install.packages("VIF")
library(VIF)
install.packages("faraway")
library(faraway)
vif(m2)

install.packages("MCMCpack")
require(MCMCpack)
yogurt.mcmc <- MCMCregress(log_quantity1 ~ log_unit_price1 + log_coupon_value1,data=style_aggregated_sorted)
summary(yogurt.mcmc)
vif(yogurt.mcmc)

yogurt.mcmc2 <- MCMCregress(log_quantity1~ log_unit_price1 + log_coupon_value1+yogurt.agg$deal_flag_uc,data=style_aggregated_sorted)
summary(yogurt.mcmc2)
vif(yogurt.mcmc2)
```
The VIF test value for each variable is close to 1, which means the multicollinearity is very low among these variables.Based on the above analysis, we can accept the regression result and construct the multi-linear model of sales as follows:
log(Sales) = 6.344 -0.7884 * log(unit_price) + 0.4531* log(coupon_value) + 1.433e-05* deal_flag_uc
```{r}
PE.unit_price<- as.numeric(mean(yogurt.mcmc2[,2]) log(mean(YOGURT_purchase$unit_price))/log(mean(YOGURT_purchase$total_price_paid)))
PE.unit_price
```
The PE indicates that 10% decrease in price will increase the sales by 3.7%, and vice verse.

```{r}
# Sales Driver Analysis and Price Elasticity Analysis for the GREEK yogurt
x <- as.POSIXct(YOGURT_purchase$purchase_date)
mo <- strftime(x, "%m")
yr <- strftime(x, "%Y")
dd <- data.frame(mo, yr, quantity=YOGURT_purchase$quantity,total_paid=YOGURT_purchase$total_price_paid,
                 coupon_value=YOGURT_purchase$coupon_value,deal_flag_uc=YOGURT_purchase$deal_flag_uc,style_descr=YOGURT_purchase$style_descr,type_descr=YOGURT_purchase$type_descr,flavor_descr=YOGURT_purchase$flavor_descr)

dd.GREEK <- dd[dd$style_descr=="GREEK",c(1:9)]

quantity.agg <- aggregate(quantity ~ mo + yr, dd.GREEK, FUN = sum)
total_price_paid.agg <- aggregate(total_paid ~ mo + yr, dd.GREEK, FUN = sum)
coupon_value.agg <- aggregate(coupon_value ~ mo + yr, dd.GREEK, FUN = sum)
deal_flag_uc.agg <- aggregate(deal_flag_uc ~ mo + yr, dd.GREEK, FUN = sum)

quantity <- as.data.frame(quantity.agg$quantity)
coupon <- as.data.frame(coupon_value.agg$coupon_value)
total_price <- as.data.frame(total_price_paid.agg$total_paid)
deal <- as.data.frame(deal_flag_uc.agg$deal_flag_uc)
GREEK.agg <- c(quantity,total_price,coupon,deal)
GREEK.agg <- as.data.frame(GREEK.agg)
GREEK.agg$unit_price <- GREEK.agg$total_price_paid.agg.total_paid/GREEK.agg$quantity.agg.quantity

# YOGURT_Greek <- YOGURT_purchase[YOGURT_purchase$style_descr=="GREEK",c(4:7,18,21)]

# YOGURT_Greek$unit_price <- YOGURT_Greek$total_price_paid/YOGURT_Greek$quantity

hist(GREEK.agg$unit_price,main="",xlab="unit price",prob=T,col="lightyellow")
hist(log(GREEK.agg$unit_price),main="",xlab="unit price",prob=T,col="lightyellow")

hist(GREEK.agg$coupon_value,main="",xlab="coupon_value",prob=T,col="lightyellow")
hist(log(GREEK.agg$coupon_value),main="",xlab="coupon_value",prob=T,col="lightyellow")

hist(GREEK.agg$quantity,main="",xlab="quantity",prob=T,col="lightyellow")
hist(log(GREEK.agg$quantity),main="",xlab="quantity",prob=T,col="lightyellow")
```

```{r}
log_quantity1 <- log(GREEK.agg$quantity+0.0001)
log_unit_price1 <- log(GREEK.agg$unit_price+0.0001)
log_coupon_value1 <- log(GREEK.agg$coupon_value+0.0001)

ml1 <- lm(log_quantity1 ~ log_unit_price1+log_coupon_value1)
summary(ml1)
vif(ml1)

ml2 <- lm(log_quantity1 ~ log_unit_price1 +log_coupon_value1+GREEK.agg$deal_flag_uc,data=GREEK.agg)
summary(ml2)
vif(ml2)
```
The VIF test value for each variable is close to 1, which means the multicollinearity is very low among these variables.Based on the above analysis, we can accept the regression result and construct the multi-linear model of sales as follows:
log(Sales) = 9.308 -0.07257 * log(unit_price) + 0.1201* log(coupon_value) + 4.903e-05* deal_flag_uc

```{r}
PE.unit_price<- as.numeric(ml2$coefficients["log_unit_price1"]*log(mean(GREEK.agg$unit_price))/log(mean(GREEK.agg$total_price_paid.agg.total_paid)))
PE.unit_price
```
The PE indicates that 10% decrease in price will increase the sales by 0.02%, and vice verse.

Usually companies want to get higher profit rather than just higher sales quantity. So, how to set the optimal price for the new Greek yogurt to get the maximum profit based on the regression model above?
To simplify the question, we can let the deal_flag_uc = 1, the unit_price = 1.531316 (mean value), and the coupon = 2503.361 (mean value).

#### Optimal Pricing and Sales Prediction
log(Sales) = 9.308 -0.07257 * log(price) + 0.1201* log(2503.361) + 4.903e-05* 1
           = 10.24788 - 0.07257*log(price)
exp(10.21695)-exp(10.21691)
(Sales <- exp(10.24788 - 0.07257*log(price)))

Assume the marginal cost(C) per unit of yogurt is 0.25*1.531316. We can calculate the profit (Y) by the following formula:
Y = (price – C) * Sales Quantity
= (price-0.382829) * exp(10.24788 - 0.07257*log(price))
= (exp(10.24788)*x-10804.45)/1.075268*log(x)


#### Optimal Coupon and Sales Prediction
log(Sales) = 9.308 -0.07257 * log(1.531316) + 0.1201* log(coupon)
           = 9.277076 + 0.1201* log(coupon)

(Sales <- exp(9.277076 + 0.1201* log(coupon)))

Assume the marginal cost(C) per unit of yogurt is 0.25*1.531316. We can calculate the profit (Y) by the following formula:
Y = (1.531316 – C) * Sales Quantity
= (1.531316-0.382829) * exp(9.277076 + 0.1201* log(coupon))
=  1.148496*exp(9.277076 + 0.1201* log(x))
```{r}
f <- function(x) 1.148496*exp(9.277076 + 0.1201* log(x))
optimize(f,lower=2000,upper=3000,maximum=TRUE)

```

```{r}
# Sales Driver Analysis and Price Elasticity Analysis for the REGULAR yogurt
x <- as.POSIXct(YOGURT_purchase$purchase_date)
mo <- strftime(x, "%m")
yr <- strftime(x, "%Y")
dd <- data.frame(mo, yr, quantity=YOGURT_purchase$quantity,total_paid=YOGURT_purchase$total_price_paid,
                 coupon_value=YOGURT_purchase$coupon_value,deal_flag_uc=YOGURT_purchase$deal_flag_uc,style_descr=YOGURT_purchase$style_descr,type_descr=YOGURT_purchase$type_descr,flavor_descr=YOGURT_purchase$flavor_descr)

dd.REGULAR <- dd[dd$style_descr=="REGULAR",c(1:9)]

quantity.agg <- aggregate(quantity ~ mo + yr, dd.REGULAR, FUN = sum)
total_price_paid.agg <- aggregate(total_paid ~ mo + yr, dd.REGULAR, FUN = sum)
coupon_value.agg <- aggregate(coupon_value ~ mo + yr, dd.REGULAR, FUN = sum)
deal_flag_uc.agg <- aggregate(deal_flag_uc ~ mo + yr, dd.REGULAR, FUN = sum)

quantity <- as.data.frame(quantity.agg$quantity)
coupon <- as.data.frame(coupon_value.agg$coupon_value)
total_price <- as.data.frame(total_price_paid.agg$total_paid)
deal <- as.data.frame(deal_flag_uc.agg$deal_flag_uc)
REGULAR.agg <- c(quantity,total_price,coupon,deal)
REGULAR.agg <- as.data.frame(REGULAR.agg)
REGULAR.agg$unit_price <- REGULAR.agg$total_price_paid.agg.total_paid/REGULAR.agg$quantity.agg.quantity

# YOGURT_Greek <- YOGURT_purchase[YOGURT_purchase$style_descr=="GREEK",c(4:7,18,21)]

# YOGURT_Greek$unit_price <- YOGURT_Greek$total_price_paid/YOGURT_Greek$quantity

hist(REGULAR.agg$unit_price,main="",xlab="unit price",prob=T,col="lightyellow")
hist(log(REGULAR.agg$unit_price),main="",xlab="unit price",prob=T,col="lightyellow")

hist(REGULAR.agg$coupon_value,main="",xlab="coupon_value",prob=T,col="lightyellow")
hist(log(REGULAR.agg$coupon_value),main="",xlab="coupon_value",prob=T,col="lightyellow")

hist(REGULAR.agg$quantity,main="",xlab="quantity",prob=T,col="lightyellow")
hist(log(REGULAR.agg$quantity),main="",xlab="quantity",prob=T,col="lightyellow")
```

```{r}
log_quantity2<- log(REGULAR.agg$quantity+0.0001)
log_unit_price2<- log(REGULAR.agg$unit_price+0.0001)
log_coupon_value2<- log(REGULAR.agg$coupon_value+0.0001)

ml1<- lm(log_quantity2~ log_unit_price2+log_coupon_value1)
summary(ml1)
vif(ml1)

ml2 <- lm(log_quantity2~ log_unit_price2+log_coupon_value2+REGULAR.agg$deal_flag_uc,data=REGULAR.agg)
summary(ml2)
vif(ml2)

PE.unit_price<- as.numeric(ml1$coefficients["log_unit_price1"]*log(mean(GREEK.agg$unit_price))/log(mean(GREEK.agg$total_price_paid.agg.total_paid)))
PE.unit_price
```
The PE indicates that 10% decrease in price will increase the sales by 2.8%, and vice verse.

```{r}
install.packages(c("lavaan", "semTools", "semPlot"))
library(lavaan)
library(semTools)
library(semPlot)


Model1 <- " quantity =~ coupon+promotion+unit_price"
colnames(REGULAR.agg) <- c("quantity","total_price","coupon","promotion","unit_price")
REGULAR.agg$quantity <- log(REGULAR.agg$quantity)
REGULAR.agg$coupon <- log(REGULAR.agg$coupon)
REGULAR.agg$promotion <- log(REGULAR.agg$promotion)
REGULAR.agg$unit_price <- log(REGULAR.agg$unit_price)

pies.fit.NH1 <- cfa(Model1, data=REGULAR.agg)
summary(pies.fit.NH1, fit.measures=TRUE)

sales.fit<- sem(Model1, data=REGULAR.agg)
summary(sales.fit, fit.measures=TRUE)
semPaths(sales.fit, what="est", fade=FALSE, residuals=FALSE,layout="tree",structural= TRUE,edge.label.cex=0.75)
```

```{r}
# Aggregated household purchase 
household.purchase <- aggregate(YOGURT_purchase[,c(4,5)],by=list(YOGURT_purchase$household_code),FUN=sum)
household.purchase$total_price_paid
household.purchase.sorted <- household.purchase[order(-household.purchase$total_price_paid),]
colnames(household.purchase.sorted)[1] <- "Household_Code"
head(household.purchase.sorted)
write.table(household.purchase.sorted, "household.purchase.sorted.csv", sep=",", na = "", row.names = FALSE)

# Analyze the household purchase and cluster information
panelist_lca <- read.csv(paste(dataPath,"panelist_lca.csv",sep='/'),header=TRUE)
cluster.purchase<- merge(panelist_lca,household.purchase.sorted,by="Household_Code")
cluster.purchase.sorted <- cluster.purchase[order(-cluster.purchase$total_price_paid),]
top.purchase <- cluster.purchase.sorted[1:10000,]
table(top.purchase$LCA_Result)

# subtract the information for the largest purchase amount household 
household.30763398 <- panelists_2012[panelists_2012$household_code==30763398,]
household.30763398

purchase.30763398 <- YOGURT_purchase[YOGURT_purchase$household_code==30763398,]
which.max(table(purchase.30763398$style_descr))
which.max(table(purchase.30763398$type_descr))
which.max(table(purchase.30763398$flavor_descr))

purchase.timesorted <- yogurt_selected[order(yogurt_selected$purchase_date),]
timebased.30763398<- purchase.timesorted[purchase.timesorted$household_code==30763398,]
write.table(timebased.30763398, "timebased.30763398.csv", sep=",", na = "", row.names = FALSE)

# Calculate and plot the monthly purchase quantity for household code 30763398
x <- as.POSIXct(timebased.30763398$purchase_date)
mo <- strftime(x, "%m")
yr <- strftime(x, "%Y")
dd <- data.frame(mo, yr, quantity=timebased.30763398$quantity,total_paid=timebased.30763398$total_price_paid)

dd.agg <- aggregate(quantity ~ mo + yr, dd, FUN = sum)
dd.agg
install.packages("plotly")
library(plotly)
ggplot(data=dd.agg,mapping=aes(x=mo,y=quantity))+geom_point()+geom_line()
# dd.agg$date <- as.POSIXct(paste(dd.agg$yr, dd.agg$mo, "01", sep = "-"))
```


