---
`title: "Nielsen Part2"
author: "Weijie Gao"
date: "May 20, 2017"
output: html_document
---

## Read the data, 2012 Nielsen Dataset
# Define the datapath
```{r}
datapath<-"C:/Users/AA/Google Drive/UChicago MscA_/Marketing Analytics/Course Project/Nielsen/2012/"
```


# Read panelist dataset
```{r}
panelists_2012 <- read.delim(file=paste(datapath,'panelists_2012.tsv',sep='/'),
                        header=TRUE, sep = "\t")

head(panelists_2012)
dim(panelists_2012)
names(panelists_2012)
```

# LCA Analysis based on Panelist Data
```{r}
library(poLCA)
library(caret)

# Columns selected for segmentation analysis

panelist.lca.data <- panelists_2012[,c(5,6,7,8,9,10,11,12,13,24,33,34,35)]
attach(panelist.lca.data)
names(panelist.lca.data)

panelist.lca.data$female_head_age_1 <- panelist.lca.data$female_head_age+1
panelist.lca.data$male_head_age_1 <- panelist.lca.data$male_head_age+1
panelist.lca.data$female_head_employment_1 <- panelist.lca.data$female_head_employment+1
panelist.lca.data$male_head_employment_1 <- panelist.lca.data$male_head_employment+1


# split data (train & test) 
set.seed(123) 
my.index<-createDataPartition(panelist.lca.data[, 1], p=0.7, times=1, list=FALSE) 

panelist.lca.train.data<-panelist.lca.data[my.index, ] 
panelist.lca.test.data<-panelist.lca.data[-my.index, ]

# choose relevant categorical variables 
my.vars.1 <- cbind(household_income,household_size,type_of_residence,household_composition,age_and_presence_of_children,female_head_age_1,male_head_age_1,female_head_employment_1,male_head_employment_1)~1

my.aic <- c(0,0,0,0,0,0,0,0,0,0) 
panelist.lca <- list()

for (i in 2:10){
    panelist.lca<- poLCA(my.vars.1, panelist.lca.train.data, nclass = i, nrep = 10,    verbose = FALSE) 
print(my.aic <- panelist.lca$aic)}


# from AIC results above, we perform scree plot 
my.aic <- c(1010560,942957.9,894243.7,875960.9,860452.1,852151.5,846096.9,843577.5,
            837989.8)

# scree plot 
class <- c(2,3,4,5,6,7,8,9,10) 
plot(x=class, y=my.aic, type="o", xlim=c(2,10), xlab="number of classes", ylab="AIC",main = "Scree Plot")

# Choose 4 clusters according to the scree plot. 

# set seed 
set.seed(123) 
# plot 
panelist.lca.4<-poLCA(my.vars.1, panelist.lca.train.data, nclass=4, nrep=50, graph=TRUE, verbose=FALSE)
```

Class1: Household income: 
```{r}
panelist.lca.4
```

```{r}
#Holdout Validation & Commentary
# set seed 
set.seed(123) 

# plot 
panelist.lca.4.test <- poLCA(my.vars.1, panelist.lca.test.data, nclass=4, nrep=50, probs.start = panelist.lca.4$probs.start, graphs=FALSE, verbose = FALSE) 

panelist.lca.4.test
```

```{r}
# Combine train and holdout together to perform the LCA. 
# set seed 
set.seed(123) 

# plot 
panelist.lca.4.all <- poLCA(my.vars.1, panelist.lca.data, nclass=4, nrep=50,  graphs=FALSE, verbose = FALSE) 

panelist.lca.4.all
```
```{r}
lca.class.result <- panelist.lca.4.all$predclass
length(lca.class.result)

lca.class.result <- cbind(Household_Code = panelists_2012$household_code,LCA_Result = lca.class.result)
dim(lca.class.result)

lca.class.result.graph <- cbind(panelists_2012,LCA_Result = lca.class.result)

write.csv(lca.class.result,file=paste(datapath,"panelist_lca.csv",sep="/"),row.names = F,quote=F)

write.csv(lca.class.result.graph,file=paste(datapath,"panelist_lca_graph.csv",sep="/"),row.names = F,quote=F)

```


# Read purchases dataset
```{r}
purchases_2012 <- read.delim(file=paste(datapath,'purchases_2012.tsv',sep='/'),
                        header=TRUE, sep = "\t")
head(purchases_2012)
names(purchases_2012)
dim(purchases_2012)
```

```{r}
trips_2012 <- read.delim(file=paste(datapath,'trips_2012.tsv',sep='/'),
                        header=TRUE, sep = "\t")
head(trips_2012)
names(trips_2012)
dim(trips_2012)
```

# Joint trips with purchases: 
```{r}
trip_purchase_2012 <- merge(x = trips_2012, y = purchases_2012, by = "trip_code_uc", all = TRUE)

head(trip_purchase_2012)
```


# Upload the data from Products: 
```{r}
products <- read.delim(file=paste(datapath,'products.tsv',sep='/'), fill= TRUE,
                        header=TRUE, sep = "\t", row.names= NULL)
head(products)
col.names <- colnames(products)
col.names

# Delete the 12th column 
products <- products[,-12]
head(products)
dim(products)

colnames(products) <- col.names[-1]
head(products)
dim(products)

products.yogurt <- products[products$product_group_descr == 'YOGURT',]
head(products.yogurt)
dim(products.yogurt)
```


```{r}
products_extra_2012 <- read.delim(file=paste(datapath,'products_extra_2012.tsv',sep='/'),
                        header=TRUE, sep = "\t")
head(products_extra_2012)
names(products_extra_2012)
dim(products_extra_2012)

products.yogurt.extra <- products_extra_2012[products_extra_2012$product_descr=='YOGURT',]
head(products.yogurt.extra)
names(products.yogurt.extra)
dim(products.yogurt.extra)
```

# Union product and product_extra table
```{r}
products.total <- merge(x = products.yogurt, y = products.yogurt.extra, by = "upc", all = TRUE)

head(products.total)
dim(products.total)

# Columns could be deleted: 
# 4.product_module_code: 3603
# 5.product_module_descr: YOGURT-REFRIGERATED
# 6.product_group_code: 2510 
# 7.product_group_descr: YOGURT
# 8. "department_code":3 
# 9. "department_descr":Dairy
# 18. "panel_year":2012 
# 21. "form_code":NA 
# 22. "form_descr"
# 23. "formula_code"
# 24. "formula_descr"
# 25: "container_code"
# 26: "container_descr" 
# 27: "salt_content_code"
# 28: "salt_content_descr" 
# 33: "product_code"
# 35: "variety_code"
# 36: "variety_descr"
# 41: "common_consumer_name_code"
# 42: "common_consumer_name_descr" 
# 43: "strength_code"
# 44: "strength_descr" 
# 45: "scent_code"
# 46: "scent_descr"
# 47: "dosage_code"
# 48: "dosage_descr"
# 49: "gender_code"
# 50: "gender_descr"
# 51: "target_skin_condition_code"
# 52: "target_skin_condition_descr"
# 53: "use_code"
# 54: "use_descr"
# 55: "size2_code" 
# 56: "size2_amount"
# 57: "size2_units"
                                          
products.total <- products.total[,-c(4:9,18,21:28,33,35:36,41:57)]
head(products.total)
dim(products.total)
```

```{r}
# Inner join trip_purchase_2012 with products_extra_2012
final.table_1 <- join(trip_purchase_2012, products_extra_2012, type = "inner", by = "upc")

head(final.table_1)
dim(final.table_1)
names(final.table_1)

# Columns that could be deleted: 
# 6. "panel_year"
# 16. "panel_year"  
# 25: "salt_content_code"
# 33: "variety_code"
# 39: "common_consumer_name_code" 
# 40: "common_consumer_name_descr" 
# 41: "strength_code"
# 42: "strength_descr"
# 43: "scent_code"
# 44: "scent_descr" 
# 45: "dosage_code"
# 46: "dosage_descr"
# 47: "gender_code"
# 48: "gender_descr"
# 49: "target_skin_condition_code" 
# 50: "target_skin_condition_descr"
# 51: "use_code"
# 52: "use_descr"

final.table_1 <- final.table_1[,-c(6,16,25,33,39:52)]
head(final.table_1)
dim(final.table_1)
```


```{r}
# Product Profile for Yogurt
length(table(final.table_1$upc))  #8562
length(table(final.table_1$flavor_code))  #776
length(table(final.table_1$flavor_descr))  #843
length(table(final.table_1$form_code)) #9  2260303 missing values
```


```{r}
brand_variations <- read.delim(file=paste(datapath,'brand_variations.tsv',sep='/'),
                        header=TRUE, sep = "\t")

head(brand_variations)
names(brand_variations)
dim(brand_variations)
```


```{r}
retailers <- read.delim(file=paste(datapath,'retailers.tsv',sep='/'),
                        header=TRUE, sep = "\t")

head(retailers)
names(retailers)
dim(retailers)
```

# Time Series Analysis
```{r}
YOGURT_2012 <- products_extra_2012[products_extra_2012$product_descr=="YOGURT",c(1:5,15:19)]

YOGURT_purchase <- merge(trip_purchase_2012,YOGURT_2012,by="upc")

# delete rows where the total price paid is 0 and there is no promotion
YOGURT_purchase <- YOGURT_purchase[!(YOGURT_purchase$total_price_paid==0&YOGURT_purchase$deal_flag_uc==0),]

YOGURT_purchase <- YOGURT_purchase[!(YOGURT_purchase$total_price_paid==0),]

# calculate the unit price of yogurt
YOGURT_purchase$unit_price <- YOGURT_purchase$total_price_paid/YOGURT_purchase$quantity


# find the index for a specific column names
grep("unit_price", colnames(YOGURT_purchase))
grep("coupon_value", colnames(YOGURT_purchase))
grep("deal_flag_uc",colnames(YOGURT_purchase))
grep("retailer_code",colnames(YOGURT_purchase))
grep("flavor_code",colnames(YOGURT_purchase))
grep("type_code",colnames(YOGURT_purchase))

# choose the selected columns
yogurt_selected <- YOGURT_purchase[,c(4,5,8,9,24,13,14,5,17,20)]

# look at the column names and their classes
sapply(yogurt_selected,class)

# change the deal_flag_uc, flavor_code, type_code into factor
yogurt_selected$deal_flag_uc <- as.factor(yogurt_selected$deal_flag_uc)
yogurt_selected$flavor_code <- as.factor(yogurt_selected$flavor_code)
yogurt_selected$type_code <- as.factor(yogurt_selected$type_code)
yogurt_selected$retailer_code <- as.factor(yogurt_selected$retailer_code)
summary(yogurt_selected)


household.purchase <- aggregate(YOGURT_purchase[,c(9,12)],by=list(YOGURT_purchase$household_code),FUN=sum)

head(household.purchase)

household.purchase.sorted <-household.purchase[order(-household.purchase$total_price_paid),]

colnames(household.purchase.sorted)[1] <- "Household_Code"

head(household.purchase.sorted)


household.30763398<- panelists_2012[panelists_2012$household_code==30763398,]
household.30763398

purchase.30763398<- YOGURT_purchase[YOGURT_purchase$household_code==30763398,]
which.max(table(purchase.30763398$type_descr))
which.max(table(purchase.30763398$flavor_descr))
```


# analyze the clusters
```{r}
panelist_lca <- read.csv(paste(datapath,"panelist_lca.csv",sep='/'),header=TRUE)

cluster.purchase<- merge(panelist_lca,household.purchase.sorted,by="Household_Code")

cluster.purchase.sorted <- cluster.purchase[order(-cluster.purchase$total_price_paid),]

top.purchase <- cluster.purchase.sorted

table(top.purchase$LCA_Result)

# The first and the second cluster purchased the most yogurt. 

```


# Time Series Analysis
```{r}
purchase.timesorted <- YOGURT_purchase[order(YOGURT_purchase$purchase_date),]
head(purchase.timesorted)
names(purchase.timesorted)

timebased.30763398<- purchase.timesorted[purchase.timesorted$household_code==30763398,]
timebased.30763398

x <- as.POSIXct(timebased.30763398$purchase_date)

mo <- strftime(x, "%m")

yr <- strftime(x, "%Y")

dd <- data.frame(mo, yr,quantity=timebased.30763398$quantity,total_paid=timebased.30763398$total_price_paid)

dd.agg <- aggregate(quantity ~ mo + yr, dd, FUN = sum)
dd.agg

library(plotly)
ggplot(data=dd.agg,mapping=aes(x=mo,y=quantity))+geom_point()+geom_line()
# dd.agg$date <- as.POSIXct(paste(dd.agg$yr, dd.agg$mo, "01", sep = "-"))


# Total sales aggregate by different periods. 
# Daily Data
period.purchase.daily <- aggregate(YOGURT_purchase[,c(9,11,12,13)],by=list(YOGURT_purchase$purchase_date),FUN=sum)

dim(period.purchase.daily)  # 364, 5
colnames(period.purchase.daily)[1] <- "date"
head(period.purchase.daily)

library(xts)
library(chron)
library(epitools)
library(TSA)
library(tseries)
library(forecast)
library(zoo)

# Clean the data for daily and weekly in xts format: 
temp.daily.time <- as.POSIXct(as.character(period.purchase.daily$date))

period.quantity.daily.xts <- xts(x=as.numeric(period.purchase.daily$quantity), order.by=temp.daily.time) 
period.quantity.weekly.xts <- apply.weekly(xts(period.quantity.daily.xts),mean)


# Quantity plot: 
plot.ts(period.quantity.daily.xts)
plot.ts(period.quantity.weekly.xts)
tsdisplay(period.quantity.daily.xts)
tsdisplay(period.quantity.weekly.xts)


# Train and holdout split: 
# daily: train dataset: Jan to Nov, test dataset: Dec
# monthly: train dataset: Jan to Nov, test dataset: Dec
# Quantity: 
quantity.daily.train <- period.quantity.daily.xts[1:335,]
quantity.daily.test <- period.quantity.daily.xts[336:364,]
quantity.weekly.train <- period.quantity.weekly.xts[1:48,]
quantity.weekly.test <- period.quantity.weekly.xts[49:53,]

# total_spent
total_spent.daily.train <- period.total_spent.daily.xts[1:335,]
total_spent.daily.test <- period.total_spent.daily.xts[336:364,]
total_spent.weekly.train <- period.total_spent.weekly.xts[1:48,]
total_spent.weekly.test <- period.total_spent.weekly.xts[49:53,]

# total_price_paid
total_price_paid.daily.train <- period.total_price_paid.daily.xts[1:335,]
total_price_paid.daily.test <- period.total_price_paid.daily.xts[336:364,]
total_price_paid.weekly.train <- period.total_price_paid.weekly.xts[1:48,]
total_price_paid.weekly.test <- period.total_price_paid.weekly.xts[49:53,]

# coupon_value
coupon_value.daily.train <- period.coupon_value.daily.xts[1:335,]
coupon_value.daily.test <- period.coupon_value.daily.xts[336:364,]
coupon_value.weekly.train <- period.coupon_value.weekly.xts[1:48,]
coupon_value.weekly.test <- period.coupon_value.weekly.xts[49:53,]



# Prediction: 
# ARIMA 
# Quantity: 
quantity_pred.dec = list()
quantity_pred.weekly.dec = list()

# Daily Prediction
arima.quantity.daily <- auto.arima(ts(quantity.daily.train), allowdrift = FALSE, stepwise = FALSE, approximation = FALSE)

summary(arima.quantity.daily)

acf(arima.quantity.daily$residuals,lag=300)


(quantity_pred.dec$arima <- forecast(arima.quantity.daily,h=29)$mean)

quantity_pred.dec.arima <- forecast(arima.quantity.daily,29)

plot(quantity_pred.dec.arima)
lines(x=c(336:364), y = quantity.daily.test, col = "red") 

# Weekly Prediction
arima.quantity.weekly <- auto.arima(ts(quantity.weekly.train), allowdrift = FALSE, stepwise = FALSE, approximation = FALSE)

summary(arima.quantity.weekly)

acf(arima.quantity.weekly$residuals,lag=300)

(quantity_pred.weekly.dec$arima <- forecast(arima.quantity.weekly,h=5)$mean)

quantity_pred.weekly.dec.arima <- forecast(arima.quantity.weekly,5)

plot(quantity_pred.weekly.dec.arima)
lines(x=c(49:53), y = quantity.weekly.test, col = "red") 

# SARIMA
# Quantity
# Daily Predition
sarima.quantity.daily <- auto.arima(ts(quantity.daily.train, frequency = 52), allowdrift = FALSE)

summary(sarima.quantity.daily)

acf(sarima.quantity.daily$residuals, lag = 300)

(quantity_pred.dec$sarima <- forecast(sarima.quantity.daily, h=29)$mean)

quantity_pred.dec.sarima <- forecast(sarima.quantity.daily,29)

plot(quantity_pred.dec.sarima)
#lines(x=c(7:8), y = Beijing.Holdout.monthly.df$values, col = "red")

# Weekly Prediction
sarima.quantity.weekly <- auto.arima(ts(quantity.weekly.train, frequency = 52), allowdrift = FALSE)

summary(sarima.quantity.weekly)

acf(sarima.quantity.weekly$residuals, lag = 300)

(quantity_pred.weekly.dec$sarima <- forecast(sarima.quantity.weekly, h=5)$mean)

quantity_pred.weekly.dec.sarima <- forecast(sarima.quantity.weekly,5)

plot(quantity_pred.weekly.dec.sarima)
#lines(x=c(7:8), y = Beijing.Holdout.monthly.df$values, col = "red")



# GARCH
# Quantity
# Daily Prediction
garch.quantity.daily <- garch(quantity.daily.train)
summary(garch.quantity.daily)

(quantity_pred.dec$garch <- (predict(garch.quantity.daily, n.ahead=29)[2:30,1]))

matplot(x = 1:364, y=c(as.numeric(quantity.daily.train), quantity_pred.dec$garch), xlab = "Month", ylab = "Quantity", col=c("black", "blue"), type = "l")
        lines(x = c(336:364), y = quantity.daily.test, col = "red")     

acf(residuals(garch.quantity.daily)[-1], lag = 300)


# Weekly Prediction
garch.quantity.weekly <- garch(quantity.weekly.train)
summary(garch.quantity.weekly)

(quantity_pred.weekly.dec$garch <- (predict(garch.quantity.weekly, n.ahead=5)[2:6,1]))

matplot(x = 1:53, y=c(as.numeric(quantity.weekly.train), quantity_pred.weekly.dec$garch), xlab = "Week", ylab = "Quantity", col=c("black", "blue"), type = "l")
lines(x = c(49:53), y = quantity.weekly.test, col = "red")     

acf(residuals(garch.quantity.weekly)[-1], lag = 300)

# Daily Prediction of Quantity
# Compare SMAPE of different models: SARIMA is the best 
smape <- function(fitted, actual) {
  return(2*mean(abs(fitted - actual) / (abs(fitted) + abs(actual))))
}

(smape.quantity_pred.dec <- mapply(smape, quantity_pred.dec, list(quantity.daily.test)))

smape.quantity_pred.dec[which.min(smape.quantity_pred.dec)]


# Weekly Prediction of Quantity
# Compare SMAPE of different models: ARIMA is the best 
(smape.quantity_pred.weekly.dec <- mapply(smape, quantity_pred.weekly.dec, list(quantity.weekly.test)))

smape.quantity_pred.weekly.dec[which.min(smape.quantity_pred.weekly.dec)]


# Daily Prediction of Quantity
#Compare MSE of different models: SARIMA is the best 
mse <- function(fitted,actual){
    return(mean((fitted-actual)^2))
}
(mse.quantity_pred.dec <- mapply(mse,quantity_pred.dec,list(quantity.daily.test)))
mse.quantity_pred.dec[which.min(mse.quantity_pred.dec)]

# Weekly Prediction of Quantity: ARIMA is the best 
(mse.quantity_pred.weekly.dec <- mapply(mse,quantity_pred.weekly.dec,list(quantity.weekly.test)))
mse.quantity_pred.weekly.dec[which.min(mse.quantity_pred.weekly.dec)]
```


# Predict the quantity for the greek yogurt
```{r}
# Total sales aggregate by different periods. 
# Daily Data
greek_purchase <- YOGURT_purchase[YOGURT_purchase$style_descr=='GREEK',]

greek.daily <- aggregate(greek_purchase[,11],by=list(greek_purchase$purchase_date),FUN=sum)

dim(greek.daily)  # 364, 2
colnames(greek.daily) <- c("date","quantity")
head(greek.daily)


# Clean the data for daily and weekly in xts format: 
greek.daily.xts <- xts(x=as.numeric(greek.daily$quantity), order.by=temp.daily.time) 
greek.weekly.xts <- apply.weekly(xts(greek.daily.xts),mean)


# Quantity plot: 
plot.ts(greek.daily.xts)
plot.ts(greek.weekly.xts)
tsdisplay(greek.daily.xts)
tsdisplay(greek.weekly.xts)


# Train and holdout split: 
# daily: train dataset: Jan to Nov, test dataset: Dec
# monthly: train dataset: Jan to Nov, test dataset: Dec
# Quantity: 
greek.daily.train <- greek.daily.xts[1:335,]
greek.daily.test <- greek.daily.xts[336:364,]
greek.weekly.train <- greek.weekly.xts[1:48,]
greek.weekly.test <- greek.weekly.xts[49:53,]



# Prediction: 
# ARIMA 
# Quantity: 
greek.daily.dec = list()
greek.weekly.dec = list()

# Daily Prediction
arima.greek.daily.pred <- auto.arima(ts(greek.daily.train), allowdrift = FALSE, stepwise = FALSE, approximation = FALSE)

summary(arima.greek.daily.pred)

acf(arima.greek.daily.pred$residuals,lag=300)

(greek.daily.dec$arima <- forecast(arima.greek.daily.pred,h=29)$mean)

greek.daily.dec.arima <- forecast(arima.greek.daily.pred,29)

plot(greek.daily.dec.arima)
lines(x=c(336:364), y = greek.daily.test, col = "red") 


# Weekly Prediction
arima.greek.weekly.pred <- auto.arima(ts(greek.weekly.train), allowdrift = FALSE, stepwise = FALSE, approximation = FALSE)

summary(arima.greek.weekly.pred)

acf(arima.greek.weekly.pred$residuals,lag=300)

(greek.weekly.dec$arima <- forecast(arima.greek.weekly.pred,h=5)$mean)

greek.weekly.dec.arima <- forecast(arima.greek.weekly.pred,5)

plot(greek.weekly.dec.arima)
lines(x=c(49:53), y = greek.weekly.test, col = "red") 


# SARIMA
# Quantity
# Daily Predition
sarima.greek.daily.pred <- auto.arima(ts(greek.daily.train, frequency = 52), allowdrift = FALSE)

summary(sarima.greek.daily.pred)

acf(sarima.greek.daily.pred$residuals, lag = 300)

(greek.daily.dec$sarima <- forecast(sarima.greek.daily.pred, h=29)$mean)

greek.daily.dec.sarima <- forecast(sarima.greek.daily.pred,29)

plot(greek.daily.dec.sarima)
#lines(x=c(7:8), y = Beijing.Holdout.monthly.df$values, col = "red")

# Weekly Prediction
sarima.greek.weekly.pred <- auto.arima(ts(greek.weekly.train, frequency = 52), allowdrift = FALSE)

summary(sarima.greek.weekly.pred)

acf(sarima.greek.weekly.pred$residuals, lag = 300)

(greek.weekly.dec$sarima <- forecast(sarima.greek.weekly.pred, h=5)$mean)

greek.weekly.dec.sarima <- forecast(sarima.greek.weekly.pred,5)

plot(greek.weekly.dec.sarima)
#lines(x=c(7:8), y = Beijing.Holdout.monthly.df$values, col = "red")



# GARCH
# Quantity
# Daily Prediction
garch.greek.daily.pred <- garch(greek.daily.train)
summary(garch.greek.daily.pred)

(greek.daily.dec$garch <- (predict(garch.greek.daily.pred, n.ahead=29)[2:30,1]))

matplot(x = 1:364, y=c(as.numeric(greek.daily.train), greek.daily.dec$garch), xlab = "Daily", ylab = "Quantity", col=c("black", "blue"), type = "l")
lines(x = c(336:364), y = greek.daily.test, col = "red")     

acf(residuals(garch.greek.daily.pred)[-1], lag = 300)


# Weekly Prediction
garch.greek.weekly.pred <- garch(greek.weekly.train)
summary(garch.greek.weekly.pred)

(greek.weekly.dec$garch <- (predict(garch.greek.weekly.pred, n.ahead=5)[2:6,1]))

matplot(x = 1:53, y=c(as.numeric(greek.weekly.train), greek.weekly.dec$garch), xlab = "Week", ylab = "Quantity", col=c("black", "blue"), type = "l")
lines(x = c(49:53), y = greek.weekly.test, col = "red")     

acf(residuals(garch.greek.weekly.pred)[-1], lag = 300)


# SMAPE: 
# Daily Prediction of Quantity of Greek Yogurt: ARIMA is best 
(smape.greek.daily.dec <- mapply(smape, greek.daily.dec, list(greek.daily.test)))
smape.greek.daily.dec[which.min(smape.greek.daily.dec)]
# Weekly Prediction of Quantity of Greek Yogurt: ARIMA is best 
(smape.greek.weekly.dec <- mapply(smape, greek.weekly.dec, list(greek.weekly.test)))
smape.greek.weekly.dec[which.min(smape.greek.weekly.dec)]

# MSE
# Daily Prediction of Quantity of Greek Yogurt: SARIMA is best 
(mse.greek.daily.dec <- mapply(mse,greek.daily.dec,list(greek.daily.test)))
mse.greek.daily.dec[which.min(mse.greek.daily.dec)]
# Weekly Prediction of Quantity: ARIMA is the best 
(mse.greek.weekly.dec <- mapply(mse,greek.weekly.dec,list(greek.weekly.test)))
mse.greek.weekly.dec[which.min(mse.greek.weekly.dec)]
```



# Predict the quantity for the regular yogurt
```{r}
# Total sales aggregate by different periods. 
# Daily Data
regular_purchase <- YOGURT_purchase[YOGURT_purchase$style_descr=='REGULAR',]
regular.daily <- aggregate(regular_purchase[,11],by=list(regular_purchase$purchase_date),FUN=sum)

dim(regular.daily)  # 364, 2
colnames(regular.daily) <- c("date","quantity")
head(regular.daily)


# Clean the data for daily and weekly in xts format: 
regular.daily.xts <- xts(x=as.numeric(regular.daily$quantity), order.by=temp.daily.time) 
regular.weekly.xts <- apply.weekly(xts(regular.daily.xts),mean)


# Quantity plot: 
plot.ts(regular.daily.xts)
plot.ts(regular.weekly.xts)
tsdisplay(regular.daily.xts)
tsdisplay(regular.weekly.xts)


# Train and holdout split: 
# daily: train dataset: Jan to Nov, test dataset: Dec
# monthly: train dataset: Jan to Nov, test dataset: Dec
# Quantity: 
regular.daily.train <- regular.daily.xts[1:335,]
regular.daily.test <- regular.daily.xts[336:364,]
regular.weekly.train <- regular.weekly.xts[1:48,]
regular.weekly.test <- regular.weekly.xts[49:53,]



# Prediction: 
# ARIMA 
# Quantity: 
regular.daily.dec = list()
regular.weekly.dec = list()

# Daily Prediction
arima.regular.daily.pred <- auto.arima(ts(regular.daily.train), allowdrift = FALSE, stepwise = FALSE, approximation = FALSE)

summary(arima.regular.daily.pred)

acf(arima.regular.daily.pred$residuals,lag=300)

(regular.daily.dec$arima <- forecast(arima.regular.daily.pred,h=29)$mean)

regular.daily.dec.arima <- forecast(arima.regular.daily.pred,29)

plot(regular.daily.dec.arima)
lines(x=c(336:364), y = regular.daily.test, col = "red") 


# Weekly Prediction
arima.regular.weekly.pred <- auto.arima(ts(regular.weekly.train), allowdrift = FALSE, stepwise = FALSE, approximation = FALSE)

summary(arima.regular.weekly.pred)

acf(arima.regular.weekly.pred$residuals,lag=300)

(regular.weekly.dec$arima <- forecast(arima.regular.weekly.pred,h=5)$mean)

regular.weekly.dec.arima <- forecast(arima.regular.weekly.pred,5)

plot(regular.weekly.dec.arima)
lines(x=c(49:53), y = regular.weekly.test, col = "red") 


# SARIMA
# Quantity
# Daily Predition
sarima.regular.daily.pred <- auto.arima(ts(regular.daily.train, frequency = 52), allowdrift = FALSE)

summary(sarima.regular.daily.pred)

acf(sarima.regular.daily.pred$residuals, lag = 300)

(regular.daily.dec$sarima <- forecast(sarima.regular.daily.pred, h=29)$mean)

regular.daily.dec.sarima <- forecast(sarima.regular.daily.pred,29)

plot(regular.daily.dec.sarima)
#lines(x=c(7:8), y = Beijing.Holdout.monthly.df$values, col = "red")

# Weekly Prediction
sarima.greek.weekly.pred <- auto.arima(ts(greek.weekly.train, frequency = 52), allowdrift = FALSE)

summary(sarima.greek.weekly.pred)

acf(sarima.greek.weekly.pred$residuals, lag = 300)

(greek.weekly.dec$sarima <- forecast(sarima.greek.weekly.pred, h=5)$mean)

greek.weekly.dec.sarima <- forecast(sarima.greek.weekly.pred,5)

plot(greek.weekly.dec.sarima)
#lines(x=c(7:8), y = Beijing.Holdout.monthly.df$values, col = "red")



# GARCH
# Quantity
# Daily Prediction
garch.regular.daily.pred <- garch(regular.daily.train)
summary(garch.regular.daily.pred)

(regular.daily.dec$garch <- (predict(garch.regular.daily.pred, n.ahead=29)[2:30,1]))

matplot(x = 1:364, y=c(as.numeric(regular.daily.train), regular.daily.dec$garch), xlab = "Daily", ylab = "Quantity", col=c("black", "blue"), type = "l")
lines(x = c(336:364), y = regular.daily.test, col = "red")     

acf(residuals(garch.regular.daily.pred)[-1], lag = 300)


# Weekly Prediction
garch.regular.weekly.pred <- garch(regular.weekly.train)
summary(garch.greek.weekly.pred)

(greek.weekly.dec$garch <- (predict(garch.greek.weekly.pred, n.ahead=5)[2:6,1]))

matplot(x = 1:53, y=c(as.numeric(greek.weekly.train), greek.weekly.dec$garch), xlab = "Week", ylab = "Quantity", col=c("black", "blue"), type = "l")
lines(x = c(49:53), y = greek.weekly.test, col = "red")     

acf(residuals(garch.greek.weekly.pred)[-1], lag = 300)


# SMAPE: 
# Daily Prediction of Quantity of Greek Yogurt: SARIMA is best 
(smape.regular.daily.dec <- mapply(smape, regular.daily.dec, list(regular.daily.test)))
smape.regular.daily.dec[which.min(smape.regular.daily.dec)]
# Weekly Prediction of Quantity of Greek Yogurt: ARIMA is best 
(smape.regular.weekly.dec <- mapply(smape, regular.weekly.dec, list(regular.weekly.test)))
smape.regular.weekly.dec[which.min(smape.regular.weekly.dec)]

# MSE
# Daily Prediction of Quantity of Greek Yogurt: SARIMA is best 
(mse.regular.daily.dec <- mapply(mse,regular.daily.dec,list(regular.daily.test)))
mse.regular.daily.dec[which.min(mse.regular.daily.dec)]
# Weekly Prediction of Quantity: ARIMA is the best 
(mse.regular.weekly.dec <- mapply(mse,regular.weekly.dec,list(regular.weekly.test)))
mse.regular.weekly.dec[which.min(mse.regular.weekly.dec)]
```
